---
title: "Beta_intero_analysis"
output:
  word_document: default
  html_document: default
date: "2024-08-10"
---

## here we do the same analysis as for the submission but investigate what happens if we include a measures of heart rate varability and average heart rate across the task for both tasks.

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
pacman::p_load(cmdstanr, tidyverse,posterior, bayesplot, tidybayes,grid,ez,
               lsmeans, brms,lmerTest,glmmTMB,sjPlot,ggeffects, patchwork, cowplot,ggpubr,flextable, ordinal)


source(here::here("scripts","plots.R"))
```

## HRD analysis
```{r, fig.width=10, fig.height=10}
z_score = function(x){
  return((x - mean(x)) / sd(x))
}

hrd1 = read.csv(here::here("data","HRD_trial_level_data.csv"))

data <- hrd1 %>%
  mutate(
    resp = ifelse(Decision == "More", 1, 0),
    condition = as.numeric(drugs),
    BISO_vs_PLACEBO = case_when(
      drugs == "PLACEBO" ~ 0,
      drugs == "BISO" ~ 1,
      drugs == "PROP" ~ 0,
      TRUE ~ NA_real_  # Use NA_real_ for numeric NA
    ),
    PROP_vs_PLACEBO = case_when(
      drugs == "PLACEBO" ~ 0,
      drugs == "BISO" ~ 0,
      drugs == "PROP" ~ 1,
      TRUE ~ NA_real_  # Use NA_real_ for numeric NA
    ),
    
  ) %>%  mutate(trials = 1:n()) %>% 
  select(resp, drugs, subject, Alpha, trials, BISO_vs_PLACEBO,PROP_vs_PLACEBO,listenBPM,Confidence,ResponseCorrect) %>%
  # drop_na() %>%
  mutate(sub = as.numeric(as.factor(subject)))
```

## Plotting each subject data and the binominal regression:
```{r, warning=F, error=F, fig.width=10,fig.height=8}
data %>% drop_na() %>% group_by(Alpha,subject,drugs) %>% summarize(prop = sum(resp)/n(), n = n()) %>% 
    ggplot(aes(x = Alpha, y = prop, col = drugs))+geom_point(aes(size = n))+
  theme_classic()+
   geom_smooth(method = "glm", 
    method.args = list(family = "binomial"), 
    se = FALSE)+
  facet_wrap(~subject)

data %>% drop_na() %>% group_by(Alpha,subject,drugs) %>% 
  filter(ResponseCorrect == "True") %>% 
  summarize(prop = mean(Confidence), se = sd(Confidence)/sqrt(n())) %>% 
    ggplot(aes(x = Alpha, y = prop, col = drugs))+
    geom_point(shape = 21, col = "black", alpha = 0.3)+
  theme_classic()+
  geom_smooth(se = F)+
  scale_y_continuous(limits = c(0,100))+
  facet_wrap(~subject)

data %>% drop_na() %>% group_by(Alpha,subject,drugs) %>% 
  filter(ResponseCorrect == "False") %>% 
  summarize(prop = mean(Confidence), se = sd(Confidence)/sqrt(n())) %>% 
    ggplot(aes(x = Alpha, y = prop, fill = drugs, col = drugs))+
  geom_point(shape = 21, col = "black", alpha = 0.3)+
  theme_classic()+
  geom_smooth(se = F)+
  scale_y_continuous(limits = c(0,100))+
  facet_wrap(~subject)
```

## fit the psychometric function
```{r, fig.width=10, fig.height=10}
# first two (bad data) last one due to unblinding

outliers_hrd = c("sub_4043","sub_4024","sub_4049")

mod = cmdstanr::cmdstan_model(here::here("scripts","stanmodels","revisions","HRD_none.stan"),stanc_options = list("O1"))

avg_hr = data %>% group_by(drugs,sub) %>% 
  summarise(avg_hr = mean(listenBPM),
            sd_hr = sd(listenBPM)) %>% 
  ungroup() %>% 
  mutate(avg_hr = z_score(avg_hr),
         sd_hr = z_score(sd_hr))

data = inner_join(avg_hr,data)

df1_nooutlier = data %>% filter(!subject %in% outliers_hrd) %>% 
  mutate(sub = as.numeric(as.factor(sub)))%>% 
  arrange(sub,drugs) %>% 
  group_by(sub,drugs) %>% 
  mutate(trials_per_id = 1:n()) %>% 
  ungroup() %>% 
  mutate(full_trials = 1:n(), trials = NULL)

# write.csv(df1_nooutlier,here::here("data","cleaned","HRD.csv"))

datastan = list(T = nrow(df1_nooutlier),
                S = length(unique(df1_nooutlier$sub)),
                S_id = as.numeric(df1_nooutlier$sub),
                X = df1_nooutlier %>% .$Alpha,
                X_lapse = (as.matrix((data.frame(int = rep(1,nrow(df1_nooutlier)),
                                                 placebo_vs_biso = df1_nooutlier %>% .$BISO_vs_PLACEBO,
                                                 placebo_vs_prop = df1_nooutlier %>% .$PROP_vs_PLACEBO)))),
                
                X_alpha = (as.matrix((data.frame(int = rep(1,nrow(df1_nooutlier)),
                                                 placebo_vs_biso = df1_nooutlier %>% .$BISO_vs_PLACEBO,
                                                 placebo_vs_prop = df1_nooutlier %>% .$PROP_vs_PLACEBO
                                                 # avg_hr = df1_nooutlier %>% .$avg_hr
                                                 # sd_hr = df1_nooutlier$sd_hr
                                                 )))),
                
                X_beta = (as.matrix((data.frame(int = rep(1,nrow(df1_nooutlier)),
                                                placebo_vs_biso = df1_nooutlier %>% .$BISO_vs_PLACEBO,
                                                placebo_vs_prop = df1_nooutlier %>% .$PROP_vs_PLACEBO
                                                # avg_hr = df1_nooutlier %>% .$avg_hr
                                                # sd_hr = df1_nooutlier$sd_hr
                                                )))),
                N_alpha = 3,
                N_beta = 3,
                N_lapse = 3,
                
                Y = df1_nooutlier  %>% .$resp
                
)

## fitting
HRD_none <- mod$sample(
  data = datastan,
  iter_sampling = 2500,
  iter_warmup = 2500,
  chains = 4,
  init = 0,
  parallel_chains = 4,
  refresh = 50,
  adapt_delta = 0.99,
  max_treedepth = 12
)
HRD_none$save_object(here::here("STAN models","HRD_none.RDS"))  

if(dir.exists(here::here("STAN models"))){
  HRD_double$save_object(here::here("STAN models","HRD_full.RDS"))  
}else{
  dir.create(here::here("STAN models"))
  HRD$save_object(here::here("STAN models","HRD.RDS"))
}


## Threshold
HRD$summary(c("gm[2]","gm[3]"))
as_draws_df(HRD$draws(c("gm[2]","gm[3]"))) %>% select(-contains(".")) %>% 
  pivot_longer(everything()) %>% group_by(name) %>% summarize(1-sum(value>0)/n())

## Slopes
HRD$summary(c("gm[6]","gm[7]"))
as_draws_df(HRD$draws(c("gm[6]","gm[7]"))) %>% select(-contains(".")) %>% 
  pivot_longer(everything()) %>% group_by(name) %>% summarize(1-sum(value>0)/n())

## Lapse rate
HRD$summary(c("gm[10]","gm[11]"))
as_draws_df(HRD$draws(c("gm[10]","gm[11]"))) %>% select(-contains(".")) %>% 
  pivot_longer(everything()) %>% group_by(name) %>% summarize(1-sum(value>0)/n())

```


## RRST:

### load data
```{r}
rrst = read.csv(here::here("data","RRST_trial_level_data.csv"))

data <- rrst %>%
  mutate(
    sub = as.numeric(as.factor(subject)),
    condition = as.numeric(drugs),
    BISO_vs_PLACEBO = case_when(
      drugs == "PLACEBO" ~ 0,
      drugs == "BISO" ~ 1,
      drugs == "PROP" ~ 0,
      TRUE ~ NA_real_  # Use NA_real_ for numeric NA
    ),
    PROP_vs_PLACEBO = case_when(
      drugs == "PLACEBO" ~ 0,
      drugs == "BISO" ~ 0,
      drugs == "PROP" ~ 1,
      TRUE ~ NA_real_  # Use NA_real_ for numeric NA
    ),
    
  ) %>%  mutate(trials = 1:n()) %>% 
  select(Resp, drugs, subject, sub, Stim, trials, BISO_vs_PLACEBO,PROP_vs_PLACEBO, ConfResp,RespLR) %>%
  drop_na() %>%
  mutate(sub = as.numeric(as.factor(subject)))
```

# plot psychometric
```{r, warning=F, error=F, fig.width=10,fig.height=8}
data %>% drop_na() %>% 
  group_by(Stim,subject,drugs) %>% 
  mutate(ACC = Resp == RespLR) %>% 
  summarize(prop = sum(Resp)/n(), n = n()) %>% 
    ggplot(aes(x = Stim, y = prop, col = drugs))+geom_point(aes(size = n))+
  theme_classic()+
   geom_smooth(method = "glm", 
    method.args = list(family = "binomial"), 
    se = FALSE)+
  facet_wrap(~subject)
```



### fit data

```{r, fig.width=10, fig.height=10}

# again 3 random responses and last unblinded
badids = c("sub_4024","sub_4077","sub_4072","sub_4049")


df1_remove_outlier = data %>% filter(!subject %in% badids)


df1_remove_outlier = df1_remove_outlier %>% mutate(sub = as.numeric(as.factor(sub))) %>% 
  arrange(sub,drugs) %>% group_by(sub,drugs) %>% 
  mutate(trials_per_id = 1:n()) %>% ungroup() %>% mutate(full_trials = 1:n(), trials = NULL)

write.csv(df1_remove_outlier,here::here("data","cleaned","RRST.csv"))


df1_remove_outlier = inner_join(avg_hr,df1_remove_outlier)


RRST = cmdstanr::cmdstan_model(here::here("scripts","stanmodels","revisions","RRST_doublecontrol.stan"),stanc_options = list("O1"))

datastan = list(T = nrow(df1_remove_outlier),
                S = length(unique(df1_remove_outlier$sub)),
                S_id = (df1_remove_outlier$sub),
                X = df1_remove_outlier %>% .$Stim,
                X_lapse = t(as.matrix((data.frame(int = rep(1,nrow(df1_remove_outlier)),
                                                placebo_vs_biso = df1_remove_outlier %>% .$BISO_vs_PLACEBO,
                                                placebo_vs_prop = df1_remove_outlier %>% .$PROP_vs_PLACEBO)))),
                
                X_alpha = t(as.matrix((data.frame(int = rep(1,nrow(df1_remove_outlier)),
                                                placebo_vs_biso = df1_remove_outlier %>% .$BISO_vs_PLACEBO,
                                                placebo_vs_prop = df1_remove_outlier %>% .$PROP_vs_PLACEBO,
                                                avg_hr = df1_remove_outlier %>% .$avg_hr,
                                                sd_hr = df1_remove_outlier$sd_hr
                                                 )))),

                X_beta = t(as.matrix((data.frame(int = rep(1,nrow(df1_remove_outlier)),
                                                placebo_vs_biso = df1_remove_outlier %>% .$BISO_vs_PLACEBO,
                                                placebo_vs_prop = df1_remove_outlier %>% .$PROP_vs_PLACEBO,
                                                avg_hr = df1_remove_outlier %>% .$avg_hr,
                                                 sd_hr = df1_remove_outlier$sd_hr
                                                 )))),
                
                N_alpha = 5,
                N_beta = 5,
                N_lapse = 3,
                Y = df1_remove_outlier  %>% .$Resp
)

## fitting
RRST_control <- RRST$sample(
  data = datastan,
  iter_sampling = 2500,
  iter_warmup = 2500,
  chains = 4,
  parallel_chains = 4,
  refresh = 50,
  init = 0,
  adapt_delta = 0.99,
  max_treedepth = 12
)
RRST_control$save_object(here::here("STAN models","RRST_doublecontrol.RDS"))
if(dir.exists(here::here("STAN models"))){
  RRST_control$save_object(here::here("STAN models","RRST_control.RDS"))
}else{
  dir.create(here::here("STAN models"))
  RRST$save_object(here::here("STAN models","RRST.RDS"))
}


## Slope
RRST$summary(c("gm[2]","gm[3]"))
as_draws_df(RRST$draws(c("gm[2]","gm[3]"))) %>% select(-contains(".")) %>% 
  pivot_longer(everything()) %>% group_by(name) %>% summarize(1-sum(value>0)/n())

## Threshold
RRST$summary(c("gm[8]","gm[9]"))
as_draws_df(RRST$draws(c("gm[8]","gm[9]"))) %>% select(-contains(".")) %>% 
  pivot_longer(everything()) %>% group_by(name) %>% summarize(1-sum(value>0)/n())


## Lapse
RRST$summary(c("gm[5]","gm[6]"))
as_draws_df(RRST$draws(c("gm[5]","gm[6]"))) %>% select(-contains(".")) %>% 
  pivot_longer(everything()) %>% group_by(name) %>% summarize(1-sum(value>0)/n())


```

# Metacognition 

## Same models by check marginal effects plots with data overlaid


```{r}
RRST_trial_data <- read_csv(here::here("data","cleaned","RRST.csv")) %>% 
    filter(ConfResp >= 0 & ConfResp <= 100) %>%
    mutate(Conf = ConfResp/100,
           Stimulus = Stim,
           Drug = factor(drugs, levels = c("PLACEBO", "PROP", "BISO"), labels = c("placebo", "propranolol", "bisoprolol")),
           Drug = relevel(Drug, ref = "placebo"),
           Condition = drugs,
           Accuracy = factor(Resp, levels = c(1, 0), labels = c("Correct", "Incorrect"))
           )
  
# Cleaning RRST data
RRST_trial_data <- clean_and_report(RRST_trial_data, "RRST_trial_data")

  
## Models

# RRST - Ordered beta regression confidence model
RRST_conf_model <- glmmTMB(
  Conf ~ Stimulus + Drug * Accuracy + (1 + Stimulus + Accuracy | subject),
  data = RRST_trial_data,
  family = ordbeta(),
  control = glmmTMBControl(optCtrl = list(iter.max = 1000, eval.max = 1000))
)

# summarise effects
summary(RRST_conf_model)

P1 = (ggemmeans(RRST_conf_model, terms = c("Stimulus","Accuracy" ,"Drug")))

subj_data = RRST_trial_data %>% group_by(Accuracy, Stimulus, Drug) %>% summarize(mean = mean(Conf),
                                                                                 q5 = mean(Conf) - 2 * sd(Conf)/sqrt(n()),
                                                                                 q95 = mean(Conf) + 2 * sd(Conf)/sqrt(n())) %>% mutate(facet = Drug)

data.frame(P1) %>% 
  mutate(Accuracy = as.factor(group)) %>% 
  ggplot()+
  geom_line(aes(x = x, y = predicted, ymin = conf.low,, ymax = conf.high, fill = Accuracy))+
  geom_ribbon(aes(x = x, y = predicted, ymin = conf.low,, ymax = conf.high, fill = Accuracy), alpha = 0.25)+
  geom_pointrange(data = subj_data, aes(x = Stimulus, y = mean, ymin = q5,ymax = q95, fill = as.factor(Accuracy)), shape = 21,col = "black")+
  scale_color_manual(values = c("green","red"))+
  scale_fill_manual(values = c("green","red"))+
  facet_wrap(~facet)+
  theme_classic()


```

# HRD

```{r, fig.width=8,fig.height=8}
HRD_trl_data = read.csv(here::here("data","cleaned","HRD.csv")) %>% 
  mutate(Conf = Confidence/100,
         drugs = as.factor(drugs),
         Drug = factor(drugs, levels = c("PLACEBO", "PROP", "BISO"), labels = c("placebo", "propranolol", "bisoprolol")),
         Drug = relevel(Drug, ref = "placebo"),
         ResponseCorrect = factor(ResponseCorrect, levels = c("True", "False"), labels = c("Correct", "Incorrect")),
         BPM_scaled = scale(listenBPM),
         Condition = drugs
  ) %>% 
  filter(subject != "sub_4049")

# Cleaning HRD data
HRD_trl_data <- clean_and_report(HRD_trl_data, "HRD_trl_data")

# HRD - Ordered beta regression confidence model
HRD_conf_model <- glmmTMB(
  Conf ~ Drug * ResponseCorrect  + BPM_scaled +  (1  + ResponseCorrect + BPM_scaled | subject),
  data = HRD_trl_data,
  family = ordbeta(),
  start = list(psi = c(0, 1)),
  control = glmmTMBControl(optCtrl = list(iter.max = 1000, eval.max = 1000))
)

summary(HRD_conf_model)

p1  = (ggemmeans(HRD_conf_model, terms = c("ResponseCorrect" ,"Drug")))

subj_data = HRD_trl_data %>% 
    group_by(Drug) %>% 
  mutate(Alpha = cut(Alpha,6))%>% 
  group_by(ResponseCorrect, Alpha, Drug) %>% 
  summarize(mean = mean(Conf),
            q5 = mean(Conf) - 2 * sd(Conf)/sqrt(n()),
            q95 = mean(Conf) + 2 * sd(Conf)/sqrt(n())) %>% mutate(facet = Drug)

preds = data.frame(facet = c("placebo","placebo","propranolol","propranolol","bisoprolol","bisoprolol"),
                   Accuracy = c("Correct","Incorrect","Correct","Incorrect","Correct","Incorrect"),
                   predicted = c(0.61,0.51,0.64,0.52,0.66,0.53),
                   conf.low = c(0.56,0.45,0.59,0.45,0.61,0.46),
                   conf.high = c(0.65,0.58,0.68,0.58,0.70,0.60)) %>% mutate(x = list(seq(0,6,by = 1))) %>% unnest()



subj_data %>% 
  mutate(Accuracy = as.factor(ResponseCorrect)) %>% 
  ggplot(aes(x = Alpha, y = mean, ymin = q5,ymax = q95, fill = Accuracy))+
      geom_pointrange(aes(x = Alpha, y = mean, ymin = q5,ymax = q95, fill = Accuracy), col = "black", shape = 21, position = position_dodge(width = 0.5))+
    geom_line(data = preds,aes(x = x, y = predicted, ymin = conf.low,, ymax = conf.high, col = Accuracy))+
  geom_ribbon(data = preds,aes(x = x, y = predicted, ymin = conf.low,, ymax = conf.high, fill = Accuracy), alpha = 0.25)+
    geom_pointrange(aes(x = Alpha, y = mean, ymin = q5,ymax = q95, fill = Accuracy), col = "black", shape = 21, position = position_dodge(width = 0.5))+
  scale_color_manual(values = c("green","red"))+
  scale_fill_manual(values = c("green","red"))+
  facet_wrap(~facet,scales = "free")+
  theme_classic()+
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))




# Obtain the estimated marginal means (EMMs) for the interaction term
HRD_emm <- emmeans(HRD_conf_model, ~ Drug * ResponseCorrect)

# Conduct post-hoc pairwise comparisons with t-tests for the Drug x ResponseCorrect interaction
posthoc_tests <- pairs(HRD_emm, by = "ResponseCorrect", adjust = "holm")

# View the results of the post-hoc tests
summary(posthoc_tests)

# table_HRD = get_main_tables(HRD_conf_model,round = 2)
# table_HRD
```
