---
title: "Indi_drug"
output: html_document
date: "2024-08-10"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
pacman::p_load(cmdstanr, tidyverse,posterior, bayesplot, tidybayes, furrr,bridgesampling, brms, faux,LRO.utilities,reticulate)
```


## What does the control analysis do and does it even work in principle?

### We conceptualize it in the following manner:

### We have a set of paricipants (P) come in for 2 sessions. They get some intervention that changes they mean resting heart rate (MRHR) by some margin (HR_intervention) however the intervention might also change the threshold of the psychometric function of the HRD (real_alpha_dif). We can simulate this in the following manner:


```{r}

set.seed(123)

source(here::here("Control analysis", "Simulate_control_agent.R"))

# 20 participants
subjects = 20

HR_intervention = -5

real_alpha_dif = -5

#now we simulate the real underlying thresholds (alphas):
alphas = data.frame(cbind(realalphas_ses1 = rnorm(subjects,-10,5),
     realalphas_ses2 = rnorm(subjects,-10-real_alpha_dif,5)))

#we also need them in real BPM here we just set the avg heart rate to 55. but same as above (important)
real_thresholds = data.frame(cbind(alphas_ses1 = rnorm(subjects,55,5),
                         alphas_ses2 = rnorm(subjects,55-real_alpha_dif,5)))

#slopes of the psychometric
betas = data.frame(cbind(beta_ses1 = rlnorm(subjects,2,0.2),
                        beta_ses2 = rlnorm(subjects,2,0.2)))

#lapses of the psychoemtric
lapses = data.frame(cbind(lapse_ses1 = brms::inv_logit_scaled(rnorm(subjects,-5,0.5)),
                lapse_ses2 = brms::inv_logit_scaled(rnorm(subjects,-5,0.5))))

#this is the the avg_heart rate for each session (see the - HR_intervention) for session 2
avg_HR = data.frame(cbind(avg_HR_ses1 = rnorm(subjects,65,5),
              avg_HR_ses2 = rnorm(subjects,65 - HR_intervention,5)))

#Now we look at the alpha (thresholds) that we observe when investigating the subjects (i.e. the difference between their average HR in the task and the latent thresholds)

obs_alpha = data.frame(alpha_ses1 = avg_HR$avg_HR_ses1-real_thresholds$alphas_ses1,
                      alpha_ses2 = avg_HR$avg_HR_ses2-real_thresholds$alphas_ses2)


df = data.frame(alphas,betas,lapses,avg_HR,obs_alpha) %>% mutate(participant_id = 1:n(), trials = 60) %>%
 pivot_longer(
 cols = -c(participant_id,trials),
 names_to = c(".value", "sessions"),
 names_sep = "_ses"
) %>% arrange(sessions,participant_id) %>% mutate(sessions =as.numeric(sessions))

#we put the subjects through PSI:

dd = get_psi_stim(df)

# and gets their trial by trial stimulus values so that we can fit all subjects together hierachically and estimate the difference with and without controlling for the HR.

write.csv(dd,here::here("control analysis","test","control_example_trial.csv"))
write.csv(df,here::here("control analysis","test","control_example_subject.csv"))
dd = read.csv(here::here("control analysis","test","control_example_trial.csv"))
df = read.csv(here::here("control analysis","test","control_example_subject.csv")) %>% mutate(X = NULL)

data = inner_join(df,dd %>% dplyr::select(resp,X,participant_id,sessions,Estimatedthreshold, Estimatedslope,q5_threshold,q95_threshold,q5_slope,q95_slope), by = c("participant_id","sessions"))


mod_noncent = cmdstanr::cmdstan_model(here::here("Combined analysis","control stan","standard.stan"),stanc_options = list("O1"))

data = data %>%
 mutate(session = ifelse(sessions == 1, 0 ,1)) %>%
 mutate(subjects = subjects,
        HR_intervention = HR_intervention,
        real_alpha_dif = real_alpha_dif)

data_fit = transform_data_to_stan(data)


data_stan = list(T = nrow(data_fit),
                S = length(unique(data_fit$participant_id)),
                S_id = as.numeric(data_fit$participant_id ),
                X = data_fit %>% .$X,
                X_lapse = as.matrix(data.frame(int = rep(1,nrow(data_fit)))),
                X_alpha = as.matrix(data.frame(int = rep(1,nrow(data_fit)),
                                               session = data_fit %>% .$sessions)),
                X_beta = as.matrix(data.frame(int = rep(1,nrow(data_fit)),
                                              session = data_fit %>% .$sessions)),
                N_alpha = 2,
                N_beta = 2,
                N_lapse = 1,
                Y = data_fit %>% .$resp,
                npx = data_fit %>% .$npx
)


# fit with model here no-control

fit_norm <- mod_noncent$sample(
 data = data_stan,
 iter_sampling = 1000,
 iter_warmup = 1000,
 chains = 4,
 parallel_chains = 4,
 refresh = 500,
 adapt_delta = 0.80,
 max_treedepth = 12
)

#extract parameters

group_variables = fit_norm$summary("gm")

group_variables = group_variables %>% mutate(variable = c("beta","beta_dif","lapse","alpha","alpha_dif"))%>%
 mutate(subjects = subjects,
        HR_intervention = HR_intervention,
        real_alpha_dif = real_alpha_dif)

non_confits = fit_norm$summary(c("alpha_p","beta_p","lapse_p"))

non_confits = non_confits %>% separate(variable, into = c("name", "indices"), sep = "\\[") %>%
 separate(indices, into = c("index1", "index2"), sep = ",|\\]") %>%
 mutate(subject = as.numeric(index1),
        sessions = as.numeric(index2))%>% select(name,mean,sd,q5,q95,subject,sessions)%>%
 mutate(subjects = subjects,
        HR_intervention = HR_intervention,
        real_alpha_dif = real_alpha_dif)


diag_non_control = data.frame(fit_norm$diagnostic_summary())%>%
 mutate(subjects = subjects,
        HR_intervention = HR_intervention,
        real_alpha_dif = real_alpha_dif)

mod_control = cmdstanr::cmdstan_model(here::here("Combined analysis","control stan","control.stan"),stanc_options = list("O1"))


data_stan = list(T = nrow(data_fit),
                S = length(unique(data_fit$participant_id)),
                S_id = as.numeric(data_fit$participant_id ),
                X = data_fit %>% .$X,
                X_lapse = as.matrix(data.frame(int = rep(1,nrow(data_fit)))),
                X_alpha = as.matrix(data.frame(int = rep(1,nrow(data_fit)),
                                               session = data_fit %>% .$sessions,
                                               avghr = scale(data_fit$avg_HR)[,1])),
                X_beta = as.matrix(data.frame(int = rep(1,nrow(data_fit)),
                                              session = data_fit %>% .$sessions,
                                              avghr = scale(data_fit$avg_HR)[,1])),
                N_alpha = 3,
                N_beta = 3,
                N_lapse = 1,
                Y = data_fit %>% .$resp,
                npx = data_fit %>% .$npx
)


# fit with model here with control

fitting
fit_control <- mod_control$sample(
 data = data_stan,
 iter_sampling = 1000,
 iter_warmup = 1000,
 chains = 4,
 init = 0,
 parallel_chains = 4,
 refresh = 500,
 adapt_delta = 0.9,
 max_treedepth = 12
)

# extract parameters

diag_control = data.frame(fit_control$diagnostic_summary())%>%
 mutate(subjects = subjects,
        HR_intervention = HR_intervention,
        real_alpha_dif = real_alpha_dif)


group_variables_con = fit_control$summary("gm")

group_variables_con = group_variables_con %>% mutate(variable = c("alpha","alpha_dif","alpha_con","beta","beta_dif","beta_con","lapse"))%>%
 mutate(subjects = subjects,
        HR_intervention = HR_intervention,
        real_alpha_dif = real_alpha_dif)



confits = fit_control$summary(c("alpha_p","beta_p","lapse_p"))

confits = confits %>% separate(variable, into = c("name", "indices"), sep = "\\[") %>%
 separate(indices, into = c("index1", "index2"), sep = ",|\\]") %>%
 mutate(subject = as.numeric(index1),
        sessions = as.numeric(index2)) %>% select(name,mean,sd,q5,q95,subject,sessions)%>%
 mutate(subjects = subjects,
        HR_intervention = HR_intervention,
        real_alpha_dif = real_alpha_dif)


real_simulated = df %>% group_by(sessions) %>% summarize(mean_realalpha = mean(realalphas),se_realalpha = sd(realalphas)/sqrt(n()),
                                       mean_beta = mean(beta),se_beta = sd(beta)/sqrt(n()),
                                       mean_lapse = mean(lapse), se_lapse = sd(lapse)/sqrt(n()),
                                       mean_avg_HR = mean(avg_HR),se_avg_HR = sd(avg_HR)/sqrt(n()),
                                       mean_alpha = mean(alpha), se_alpha = sd(alpha)/sqrt(n()))%>%
 mutate(subjects = subjects,
        HR_intervention = HR_intervention,
        real_alpha_dif = real_alpha_dif)

real_simulated = real_simulated %>% select(mean_realalpha, se_realalpha) %>% mutate(id = 1:2) %>% pivot_wider(values_from = c("mean_realalpha","se_realalpha"), names_from = id) %>% mutate(dif = mean_realalpha_1 - mean_realalpha_2, dif_se = sqrt(se_realalpha_1^2 + se_realalpha_2^2))

# plot it

data.frame() %>%
 ggplot()+
 geom_pointrange(data = group_variables_con %>% filter(variable == "alpha_dif") %>%  mutate(group = "Controlled"), aes(y = -0.1, x = mean, xmin = q5, xmax = q95, col = group))+
 geom_pointrange(data = group_variables %>% filter(variable == "alpha_dif") %>%  mutate(group = "Uncontrolled"), aes(y = 0.1, x = mean, xmin = q5, xmax = q95, col = group))+
 geom_pointrange(data = real_simulated %>%  mutate(group = "Data"), aes(y = 0, x = dif, xmin = dif-2*dif_se, xmax = dif+2*dif_se, col = group))+
 ylab("")+xlab("Estimates")+theme_minimal()+
 theme(axis.ticks.y = element_blank(),
         axis.text.y = element_blank())

```



# We do see that in this case atleast we get closer to the data with the controlled. If we repeat this process over many different HR_intervention and real_alpha dif and many times for each combination we can see what happens more generally:

# here we do it from 0 to 10 in real_alpha_dif and from 0 to 15 in HR_intevention and then 100 simulations per combination:


<!-- ```{r, fig.height=10,fig.width=10} -->
<!-- results <- readRDS("~/beta-blocker/Manuscript/testing_real.RDS") -->

<!-- real_avg = map_dfr(results,1) %>% select(sessions,mean_realalpha,se_realalpha,id,subjects,real_alpha_dif,HR_intervention) %>%  -->
<!--   pivot_wider(names_from = sessions, values_from = c("mean_realalpha","se_realalpha")) %>% unnest() %>%  -->
<!--     mutate(mean_alpha_dif = mean_realalpha_1-mean_realalpha_2, se_realalpha_dif = sqrt(se_realalpha_1^2+se_realalpha_2^2)) %>%  -->
<!--     rename(alpha = mean_realalpha_1,alpha_dif = mean_alpha_dif,se_alpha_dif = se_realalpha_dif,se_alpha = se_realalpha_1) %>%  -->
<!--     select(alpha,alpha_dif,se_alpha,se_alpha_dif,id,subjects,real_alpha_dif,HR_intervention) %>% pivot_longer(cols = c("alpha","alpha_dif"), names_to = "variable", values_to = "mean") %>%  -->
<!--     pivot_longer(cols = c("se_alpha","se_alpha_dif"), names_to = "a", values_to = "se") %>% filter(row_number() %% 2 == 1) %>%  -->
<!--     mutate(a = NULL) %>% mutate(con = "Data") -->


<!-- controlled_avg = map_dfr(results,3) %>% filter(variable %in% c("alpha","alpha_dif")) %>%  -->
<!--   select(variable,mean,q5,q95,id,subjects,real_alpha_dif,HR_intervention)%>% mutate(con = T) -->
<!-- controlled_diag = map_dfr(results,4) -->


<!-- uncontrolled_avg = map_dfr(results,6)%>% filter(variable %in% c("alpha","alpha_dif")) %>%  -->
<!--   select(variable,mean,q5,q95,id,subjects,real_alpha_dif,HR_intervention) %>% mutate(con = F) -->
<!-- uncontrolled_diag = map_dfr(results,7) -->




<!-- dd = rbind(real_avg %>% mutate(q5 = mean-2*se,q95 = mean+2*se) %>% select(id,variable,mean,q5,q95,con,subjects,real_alpha_dif,HR_intervention), -->
<!--       controlled_avg %>% select(id,variable,mean,q5,q95,con,subjects,real_alpha_dif,HR_intervention), -->
<!--       uncontrolled_avg %>% select(id,variable,mean,q5,q95,con,subjects,real_alpha_dif,HR_intervention) -->
<!--       ) -->


<!-- dd %>% filter(variable == "alpha_dif") %>% rename(control = con) %>%  -->
<!--   ggplot(aes(x = control, y = mean, ymin = q5,ymax = q95, col = as.factor(control)))+ -->
<!--   geom_boxplot()+ -->
<!--   facet_grid(real_alpha_dif~HR_intervention, labeller = label_both)+theme(legend.position = "top")+ -->
<!--   ylab("Size of difference in threshold")+ -->
<!--   theme_classic()+ -->
<!--   theme(legend.position = "top")+ -->
<!--   geom_hline(yintercept = 0, linetype = 2) -->

<!-- ``` -->

# seems to work! 

