---
title: "Beta_intero_analysis"
output:
  word_document: default
  html_document: default
date: "2024-08-10"
---

# load packages and scripts

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
pacman::p_load(cmdstanr, tidyverse,posterior, bayesplot, tidybayes,grid,ez,
               lsmeans, brms,lmerTest,glmmTMB,sjPlot,ggeffects, patchwork, cowplot,ggpubr,flextable, ordinal)


source(here::here("scripts","plots.R"))

```

## HRD analysis (Psychophysics)
```{r, fig.width=10, fig.height=10}
z_score = function(x){
  return((x - mean(x)) / sd(x))
}

hrd1 = read.csv(here::here("data","HRD_trial_level_data.csv"))

data <- hrd1 %>%
  mutate(
    resp = ifelse(Decision == "More", 1, 0),
    condition = as.numeric(drugs),
    BISO_vs_PLACEBO = case_when(
      drugs == "PLACEBO" ~ 0,
      drugs == "BISO" ~ 1,
      drugs == "PROP" ~ 0,
      TRUE ~ NA_real_  # Use NA_real_ for numeric NA
    ),
    PROP_vs_PLACEBO = case_when(
      drugs == "PLACEBO" ~ 0,
      drugs == "BISO" ~ 0,
      drugs == "PROP" ~ 1,
      TRUE ~ NA_real_  # Use NA_real_ for numeric NA
    ),
    
  ) %>%  mutate(trials = 1:n()) %>% 
  select(resp, drugs, subject, Alpha, trials, BISO_vs_PLACEBO,PROP_vs_PLACEBO,listenBPM,Confidence,ResponseCorrect) %>%
  # drop_na() %>%
  mutate(sub = as.numeric(as.factor(subject)))
```

## Plotting each subject data and the binominal regression:
```{r, warning=F, error=F, fig.width=10,fig.height=8}
data %>% drop_na() %>% group_by(Alpha,subject,drugs) %>% summarize(prop = sum(resp)/n(), n = n()) %>% 
    ggplot(aes(x = Alpha, y = prop, col = drugs))+geom_point(aes(size = n))+
  theme_classic()+
   geom_smooth(method = "glm", 
    method.args = list(family = "binomial"), 
    se = FALSE)+
  facet_wrap(~subject)
```

## Plotting each subject data (confidence ratings)
```{r, warning=F, error=F, fig.width=10,fig.height=8}
data %>% drop_na() %>% group_by(Alpha,subject,drugs) %>% summarize(prop = mean(Confidence), se = sd(Confidence)/sqrt(n())) %>% 
    ggplot(aes(x = Alpha, y = prop, col = drugs))+geom_point()+
  theme_classic()+
  facet_wrap(~subject)
```

## fit the psychometric function (controlling for average HR)
```{r, fig.width=10, fig.height=10}
# first two (bad data) last one due to unblinding

outliers_hrd = c("sub_4043","sub_4024","sub_4049")

mod = cmdstanr::cmdstan_model(here::here("scripts","stanmodels","HRD_control.stan"),stanc_options = list("O1"))

avg_hr = data %>% group_by(drugs,sub) %>% summarise(avg_hr = mean(listenBPM)) %>% ungroup() %>% mutate(avg_hr = z_score(avg_hr))

data = inner_join(avg_hr,data)

df1_nooutlier = data %>% filter(!subject %in% outliers_hrd) %>% 
  mutate(sub = as.numeric(as.factor(sub)))%>% 
  arrange(sub,drugs) %>% 
  group_by(sub,drugs) %>% 
  mutate(trials_per_id = 1:n()) %>% 
  ungroup() %>% 
  mutate(full_trials = 1:n(), trials = NULL)

write.csv(df1_nooutlier,here::here("data","cleaned","HRD.csv"))

datastan = list(T = nrow(df1_nooutlier),
                S = length(unique(df1_nooutlier$sub)),
                S_id = as.numeric(df1_nooutlier$sub),
                X = df1_nooutlier %>% .$Alpha,
                X_lapse = (as.matrix((data.frame(int = rep(1,nrow(df1_nooutlier)),
                                                 placebo_vs_biso = df1_nooutlier %>% .$BISO_vs_PLACEBO,
                                                 placebo_vs_prop = df1_nooutlier %>% .$PROP_vs_PLACEBO)))),
                
                X_alpha = (as.matrix((data.frame(int = rep(1,nrow(df1_nooutlier)),
                                                 placebo_vs_biso = df1_nooutlier %>% .$BISO_vs_PLACEBO,
                                                 placebo_vs_prop = df1_nooutlier %>% .$PROP_vs_PLACEBO,
                                                 avg_hr = df1_nooutlier %>% .$avg_hr)))),
                
                X_beta = (as.matrix((data.frame(int = rep(1,nrow(df1_nooutlier)),
                                                placebo_vs_biso = df1_nooutlier %>% .$BISO_vs_PLACEBO,
                                                placebo_vs_prop = df1_nooutlier %>% .$PROP_vs_PLACEBO,
                                                avg_hr = df1_nooutlier %>% .$avg_hr)))),
                N_alpha = 4,
                N_beta = 4,
                N_lapse = 3,
                
                Y = df1_nooutlier  %>% .$resp
                
)

## fitting
HRD <- mod$sample(
  data = datastan,
  iter_sampling = 2500,
  iter_warmup = 2500,
  chains = 4,
  parallel_chains = 4,
  refresh = 50,
  adapt_delta = 0.99,
  max_treedepth = 12
)

if(dir.exists(here::here("STAN models"))){
  HRD$save_object(here::here("STAN models","HRD.RDS"))  
}else{
  dir.create(here::here("STAN models"))
  HRD$save_object(here::here("STAN models","HRD.RDS"))
}


## Threshold
HRD$summary(c("gm[2]","gm[3]"))
as_draws_df(HRD$draws(c("gm[2]","gm[3]"))) %>% select(-contains(".")) %>% 
  pivot_longer(everything()) %>% group_by(name) %>% summarize(1-sum(value>0)/n())

## Slopes
HRD$summary(c("gm[6]","gm[7]"))
as_draws_df(HRD$draws(c("gm[6]","gm[7]"))) %>% select(-contains(".")) %>% 
  pivot_longer(everything()) %>% group_by(name) %>% summarize(1-sum(value>0)/n())

## Lapse rate
HRD$summary(c("gm[10]","gm[11]"))
as_draws_df(HRD$draws(c("gm[10]","gm[11]"))) %>% select(-contains(".")) %>% 
  pivot_longer(everything()) %>% group_by(name) %>% summarize(1-sum(value>0)/n())

```


## RRST:

### load data
```{r}
rrst = read.csv(here::here("data","RRST_trial_level_data.csv"))

data <- rrst %>%
  mutate(
    sub = as.numeric(as.factor(subject)),
    condition = as.numeric(drugs),
    BISO_vs_PLACEBO = case_when(
      drugs == "PLACEBO" ~ 0,
      drugs == "BISO" ~ 1,
      drugs == "PROP" ~ 0,
      TRUE ~ NA_real_  # Use NA_real_ for numeric NA
    ),
    PROP_vs_PLACEBO = case_when(
      drugs == "PLACEBO" ~ 0,
      drugs == "BISO" ~ 0,
      drugs == "PROP" ~ 1,
      TRUE ~ NA_real_  # Use NA_real_ for numeric NA
    ),
    
  ) %>%  mutate(trials = 1:n()) %>% 
  select(Resp, drugs, subject, sub, Stim, trials, BISO_vs_PLACEBO,PROP_vs_PLACEBO, ConfResp) %>%
  drop_na() %>%
  mutate(sub = as.numeric(as.factor(subject)))
```

# plot psychometric function
```{r, warning=F, error=F, fig.width=10,fig.height=8}
data %>% drop_na() %>% group_by(Stim,subject,drugs) %>% summarize(prop = sum(Resp)/n(), n = n()) %>% 
    ggplot(aes(x = Stim, y = prop, col = drugs))+geom_point(aes(size = n))+
  theme_classic()+
   geom_smooth(method = "glm", 
    method.args = list(family = "binomial"), 
    se = FALSE)+
  facet_wrap(~subject)
```



### fit data

```{r, fig.width=10, fig.height=10}

# again 3 random responses and last unblinded
badids = c("sub_4024","sub_4077","sub_4072","sub_4049")

RRST = cmdstanr::cmdstan_model(here::here("scripts","stanmodels","RRST_gumbel.stan"),stanc_options = list("O1"))


df1_remove_outlier = data %>% filter(!subject %in% badids)


df1_remove_outlier = df1_remove_outlier %>% mutate(sub = as.numeric(as.factor(sub))) %>% 
  arrange(sub,drugs) %>% group_by(sub,drugs) %>% 
  mutate(trials_per_id = 1:n()) %>% ungroup() %>% mutate(full_trials = 1:n(), trials = NULL)

write.csv(df1_remove_outlier,here::here("data","cleaned","RRST.csv"))

datastan = list(T = nrow(df1_remove_outlier),
                S = length(unique(df1_remove_outlier$sub)),
                S_id = (df1_remove_outlier$sub),
                X = df1_remove_outlier %>% .$Stim,
                X_lapse = t(as.matrix((data.frame(int = rep(1,nrow(df1_remove_outlier)),
                                                placebo_vs_biso = df1_remove_outlier %>% .$BISO_vs_PLACEBO,
                                                placebo_vs_prop = df1_remove_outlier %>% .$PROP_vs_PLACEBO)))),
                
                X_alpha = t(as.matrix((data.frame(int = rep(1,nrow(df1_remove_outlier)),
                                                placebo_vs_biso = df1_remove_outlier %>% .$BISO_vs_PLACEBO,
                                                placebo_vs_prop = df1_remove_outlier %>% .$PROP_vs_PLACEBO)))),

                X_beta = t(as.matrix((data.frame(int = rep(1,nrow(df1_remove_outlier)),
                                                placebo_vs_biso = df1_remove_outlier %>% .$BISO_vs_PLACEBO,
                                                placebo_vs_prop = df1_remove_outlier %>% .$PROP_vs_PLACEBO)))),
                
                N_alpha = 3,
                N_beta = 3,
                N_lapse = 3,
                Y = df1_remove_outlier  %>% .$Resp
)

## fitting
RRST <- RRST$sample(
  data = datastan,
  iter_sampling = 2500,
  iter_warmup = 2500,
  chains = 4,
  parallel_chains = 4,
  refresh = 50,
  adapt_delta = 0.99,
  max_treedepth = 12
)

if(dir.exists(here::here("STAN models"))){
  RRST$save_object(here::here("STAN models","RRST.RDS"))  
}else{
  dir.create(here::here("STAN models"))
  RRST$save_object(here::here("STAN models","RRST.RDS"))
}


## Slope
RRST$summary(c("gm[2]","gm[3]"))
as_draws_df(RRST$draws(c("gm[2]","gm[3]"))) %>% select(-contains(".")) %>% 
  pivot_longer(everything()) %>% group_by(name) %>% summarize(1-sum(value>0)/n())

## Threshold
RRST$summary(c("gm[8]","gm[9]"))
as_draws_df(RRST$draws(c("gm[8]","gm[9]"))) %>% select(-contains(".")) %>% 
  pivot_longer(everything()) %>% group_by(name) %>% summarize(1-sum(value>0)/n())


## Lapse
RRST$summary(c("gm[5]","gm[6]"))
as_draws_df(RRST$draws(c("gm[5]","gm[6]"))) %>% select(-contains(".")) %>% 
  pivot_longer(everything()) %>% group_by(name) %>% summarize(1-sum(value>0)/n())


```


# Metacognition:

## RRST

### load data
```{r}
source(here::here("scripts","plots.R"))

RRST_trial_data <- read_csv(here::here("data","cleaned","RRST.csv")) %>% 
    filter(ConfResp >= 0 & ConfResp <= 100) %>%
    mutate(Conf = ConfResp/100,
           Stimulus = Stim,
           Drug = factor(drugs, levels = c("PLACEBO", "PROP", "BISO"), labels = c("placebo", "propranolol", "bisoprolol")),
           Drug = relevel(Drug, ref = "placebo"),
           Condition = drugs,
           Accuracy = factor(Resp, levels = c(1, 0), labels = c("Correct", "Incorrect"))
           ) %>%
  filter(!subject %in% c("sub_4049", "sub_4024"))

# Cleaning RRST data
RRST_trial_data <- clean_and_report(RRST_trial_data, "RRST_trial_data")
```

### Model

```{r}

# RRST - Ordered beta regression confidence model
RRST_conf_model <- glmmTMB(
  Conf ~ Stimulus + Drug * Accuracy + (1 + Stimulus + Accuracy | subject),
  data = RRST_trial_data,
  family = ordbeta(),
  control = glmmTMBControl(optCtrl = list(iter.max = 1000, eval.max = 1000))
)

# summarise effects
summary(RRST_conf_model)

```

## HRD load data

```{r}
HRD_trl_data = read.csv(here::here("data","cleaned","HRD.csv")) %>% 
  mutate(Conf = Confidence/100,
         drugs = as.factor(drugs),
         Drug = factor(drugs, levels = c("PLACEBO", "PROP", "BISO"), labels = c("placebo", "propranolol", "bisoprolol")),
         Drug = relevel(Drug, ref = "placebo"),
         ResponseCorrect = factor(ResponseCorrect, levels = c("True", "False"), labels = c("Correct", "Incorrect")),
         BPM_scaled = scale(listenBPM),
         Condition = drugs
  ) %>% 
  filter(!subject %in% c("sub_4049", "sub_4024"))

# Cleaning HRD data
HRD_trl_data <- clean_and_report(HRD_trl_data, "HRD_trl_data")
```


## HRD fit model

```{r}
# HRD - Ordered beta regression confidence model
HRD_conf_model <- glmmTMB(
  Conf ~ Drug * ResponseCorrect + BPM_scaled +  (1  + ResponseCorrect + BPM_scaled | subject),
  data = HRD_trl_data,
  family = ordbeta(),
  start = list(psi = c(0, 1)),
  control = glmmTMBControl(optCtrl = list(iter.max = 1000, eval.max = 1000))
)

summary(HRD_conf_model)


# Obtain the estimated marginal means (EMMs) for the interaction term
HRD_emm <- emmeans(HRD_conf_model, ~ Drug * ResponseCorrect)

# Conduct post-hoc pairwise comparisons with t-tests for the Drug x ResponseCorrect interaction
posthoc_tests <- pairs(HRD_emm, by = "ResponseCorrect", adjust = "holm")

# View the results of the post-hoc tests
summary(posthoc_tests)

table_HRD = get_main_tables(HRD_conf_model,round = 2)
table_HRD
```


## Survey Data Analysis

```{r}
StateSurveys_scores <- read_csv(here::here("data","StateSurveys_scores.csv"))

## Analysis of PANAS and STICSA

# Filter and select relevant columns
StateSurveys_clean <- StateSurveys_scores %>%
  select(Subject_ID, Drug, iteration, panas_positive, panas_negative, sticsa, 
         heart_rate_sensitive, heartbeat_feeling, breathing_sensitive, breathing_feeling)

# Convert relevant variables to factors
StateSurveys_clean <- StateSurveys_clean %>%
  mutate(Drug = factor(Drug, levels = c("plac", "biso", "prop")),
         Measured_Time = factor(iteration, levels = c(0, 1), labels = c("Baseline", "Post-Drug")),
         Subject_ID = factor(Subject_ID)) %>%
  filter(!Subject_ID %in% c(4024, 4049))

# Remove participants with incomplete data
StateSurveys_clean <- StateSurveys_clean %>%
  group_by(Subject_ID) %>%
  filter(!any(is.na(panas_positive) | is.na(panas_negative) | is.na(sticsa))) %>%
  ungroup()


# PANAS Positive: Repeated measures ANOVA
panas_pos_ez <- ezANOVA(
  data = StateSurveys_clean,
  dv = panas_positive,
  wid = Subject_ID,
  within = .(Drug, Measured_Time),
  detailed = TRUE,
  type = 3
)
print(panas_pos_ez)

# PANAS Negative: Repeated measures ANOVA
panas_neg_ez <- ezANOVA(
  data = StateSurveys_clean,
  dv = panas_negative,
  wid = Subject_ID,
  within = .(Drug, Measured_Time),
  detailed = TRUE,
  type = 3
)
print(panas_neg_ez)

# STICSA (Somatic Anxiety): Repeated measures ANOVA
sticsa_ez <- ezANOVA(
  data = StateSurveys_clean,
  dv = sticsa,
  wid = Subject_ID,
  within = .(Drug, Measured_Time),
  detailed = TRUE,
  type = 3
)
print(sticsa_ez)
```


```{r}
## Analysis of Interoceptive Belief Questionnaire 

ord_reg_IBQ = function(var_name, Drug, iteration, Subject_ID, var_string){
  
  # Analysis of individual IBQ items
  cat(sprintf("Model Summary for %s:\n", var_string))
  model_intero_var <- clmm(
    formula = var_name ~ Drug * iteration + (1 | Subject_ID),
    link = "probit"
  )
  summary(model_intero_var)
  
  # Predicted marginal means
  predictions_intero_var <- emmeans(model_intero_var, ~ Drug * iteration, type = "response")
  predictions_df_intero_var <- as.data.frame(predictions_intero_var)
  
  # Get estimated marginal means by Drug and iteration
  emm <- emmeans(model_intero_var, ~ iteration | Drug)
  
  # Post-hoc pairwise comparisons between post-Drug and baseline within each drug
  contrast_results <- contrast(emm, method = "pairwise", adjust = "tukey")
  
  # Display the results
  print(contrast_results)

  return(predictions_df_intero_var)

}

# Filter and select relevant columns
StateSurveys_clean <- StateSurveys_scores %>%
  select(Subject_ID, Drug, iteration, panas_positive, panas_negative, sticsa, 
         heart_rate_sensitive, heartbeat_feeling, breathing_sensitive, breathing_feeling) %>%
  drop_na(heart_rate_sensitive, heartbeat_feeling, breathing_sensitive, breathing_feeling)


# Convert relevant variables to factors
StateSurveys_clean <- StateSurveys_clean %>%
  mutate(Drug = factor(Drug, levels = c("plac", "biso", "prop"), labels = c("placebo", "propranolol", "bisoprolol")),
         Drug = relevel(Drug, ref = "placebo"),
         iteration = factor(iteration, levels = c(0, 1), labels = c("Pre-Tasks", "Post-Tasks")),
         Subject_ID = factor(Subject_ID)) %>%
  filter(!Subject_ID %in% c(4024,4049))

# Convert the scores to ordered factors
StateSurveys_clean <- StateSurveys_clean %>%
  mutate(
    breathing_feeling = factor(breathing_feeling, ordered = TRUE),
    breathing_sensitive = factor(breathing_sensitive, ordered = TRUE),
    heartbeat_feeling = factor(heartbeat_feeling, ordered = TRUE),
    heart_rate_sensitive = factor(heart_rate_sensitive, ordered = TRUE)
  )

breath_affect_preds <- ord_reg_IBQ(StateSurveys_clean$breathing_feeling, StateSurveys_clean$Drug, StateSurveys_clean$iteration, StateSurveys_clean$Subject_ID, "breathing affect")
breath_sensit_preds <- ord_reg_IBQ(StateSurveys_clean$breathing_sensitive, StateSurveys_clean$Drug, StateSurveys_clean$iteration, StateSurveys_clean$Subject_ID, "breathing sensitivity")
cardio_affect_preds <- ord_reg_IBQ(StateSurveys_clean$heartbeat_feeling, StateSurveys_clean$Drug, StateSurveys_clean$iteration, StateSurveys_clean$Subject_ID, "heartbeat affect")
cardio_sensit_preds <- ord_reg_IBQ(StateSurveys_clean$heart_rate_sensitive, StateSurveys_clean$Drug, StateSurveys_clean$iteration, StateSurveys_clean$Subject_ID, "heartbeat sensitivity")

```


```{r}
## Check Drug Blinding

# Create a new variable indicating whether the participant's guess matches the actual drug
StateSurveys_scores <- StateSurveys_scores %>%
  mutate(correct_guess = ifelse(Drug == PerceivedDrug, 1, 0)) %>% 
  filter(iteration == 0)

# Summarise by subject to calculate the proportion of correct guesses and apply a binomial test for significance
correct_guess_summary <- StateSurveys_scores %>%
  group_by(Subject_ID) %>%
  summarize(
    proportion_correct = mean(correct_guess, na.rm = TRUE),  # Proportion of correct guesses
    total_correct = sum(correct_guess, na.rm = TRUE),        # Total correct guesses
    n_sessions = n(),                                        # Total number of sessions
    binomial_test_p = map2_dbl(total_correct, n_sessions,    # Binomial test p-value
                               ~binom.test(.x, .y, p = 1/3)$p.value)
  )

# Group-level inference: Total correct guesses and total sessions across all participants
total_correct <- sum(StateSurveys_scores$correct_guess, na.rm = TRUE)
total_sessions <- nrow(StateSurveys_scores)

# Perform a binomial test to see if the overall guessing is better than chance
group_binomial_test <- binom.test(total_correct, total_sessions, p = 1/3)
group_p_value <- group_binomial_test$p.value
group_lower_ci <- group_binomial_test$conf.int[1]
group_upper_ci <- group_binomial_test$conf.int[2]
observed_rate <- round(group_binomial_test$estimate, 2)

# Summarise proportion of significant participants
significant_proportion <- correct_guess_summary %>%
  filter(binomial_test_p < 0.05) %>%
  summarize(
    total_significant_subjects = n(),  # Count of significant participants
    proportion_significant = total_significant_subjects / nrow(correct_guess_summary)  # Proportion
  )
total_significant_subjects <- significant_proportion$total_significant_subjects
proportion_significant <- round(significant_proportion$proportion_significant * 100, 2)

```


## Analysis on listen BPM

```{r}
df1_nooutlier = read.csv(here::here("data","cleaned","HRD.csv"))

df = df1_nooutlier %>% mutate(drugs = as.factor(drugs)) %>% mutate(drugs = factor(drugs, levels = c("PLACEBO", "PROP", "BISO")))

m1 = (lmer(listenBPM ~ drugs + (drugs|subject), data = df))

summary(m1)
lsmeans(m1, pairwise ~ drugs,pbkrtest.limit = 8760)
```


## Equations

$$
\begin{cases} \alpha = 1 - g(\mu - k_1),
\\ \delta = \left[g(\mu - k_1) - g(\mu - k_2)\right] \text{Beta}\big(g(\mu),\phi\big),
\\ \gamma = g(\mu - k_2). \end{cases}
$$

$$
\mu = X'\beta
$$

