---
title: "Beta_intero_plots"
output: html_document
date: "2024-08-10"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
pacman::p_load(cmdstanr, tidyverse,posterior, bayesplot, tidybayes, furrr,
               brms, faux,LRO.utilities,reticulate,
               patchwork, glmmTMB, ggplot2, ggpubr, dplyr, emmeans, ggeffects)

np <- import("numpy")
source(here::here("scripts","plots.R"))
```

## Main plots:

### Figure_1
Psychophysical models for HRD and RRST tasks from example participant
```{r}
plot_1()
```

### Figure_2
Psychophysical modelling of beta-blockade on cardioceptive and respiroceptive sensitivity (threshold, ɑ), and precision (slope, β)
```{r}
plot_2()
```

### Figure_3
Ordered Beta Regression of Metacognition in HRD and RRST tasks
```{r}
plot_3()
```

## Supplementary plots:

### S_1
Effects of drug condition on mean heart rate and HRV metrics (RMSSD and LF/HF ratio)
```{r}
plot_s1()
```


### S_2
Plot of individual predictive participant-level psychometric functions for HRD and RRST tasks
```{r}
qq = plot_s2()

qq
```
